%The Thesis Abstract is written here (and usually kept to just this page). The page is kept centered vertically so can expand into the blank space above the title too\ldots
%
In recent years there has been an increasing interest in approaches to combine formal knowledge and \textit{artificial neural networks} (NNs), called \textit{neuro-symbolic} approaches. %~\cite{neuro-symbolic-survey:2017:many-authors,neuro-symbolic-computing:2019:many-authors}.
\textit{Formal concept analysis} (FCA) is a powerful  formal tool for understanding complex data called \textit{formal context} (FC).
FCA can be used to generate a structured view of the data, typically a hierarchy of \textit{formal concepts} called \textit{concept lattice} or an ontology. It can also discover implications between some aspects of the data and generate explainable formal rules grounded on the data, which can in turn be used to construct decision systems from the data.

In this thesis, we explore ways to solve the scalability problem inherent to FCA with the hope of revealing implicit information not expressed by FCA, by using deep learning to reproduce the processes of FCA.
Recently, neural generative models for graphs have achieved great performance on the generation of specific kinds of graphs.
Therefore, we explore an approach to reproduce the formal lattice graph of FCA using generative neural models for graphs, and in particular GraphRNN.
Additionally, we develop a data agnostic embedding model for formal concepts, Bag of Attributes (BoA).
Relying on the performance of BoA, we develop an approach to generate the \textit{intents}, a description of the formal concepts.
We report experimental results on generated and real-word data to support our conclusions.